Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2021-02-09 summary.Rmd
ssc stuff

Theorem 3 provides perfect community detection given $P$. Letting $|B|$ be the 
affinity matrix for graph $G$, $G$ is partitioned into $K$ disjoint subgraphs 
that correspond to each community. Using $A$ introduces some error in the ASE, 
resulting in points that lie near subspaces but not exactly on them. Using 
results from \cite{rubindelaunchy2017statistical}, we can show that as $n$ 
grows, the ASE of $A$ approaches the ASE of $P$ and $B_{ij} \to 0$ for $i$ and 
$j$ in different clusters.

>>>>

Theorem 3 provides perfect community detection given $P$. Letting $|B|$ be the 
affinity matrix for graph $G$, $G$ is partitioned into $K$ disjoint subgraphs 
that correspond to each community. Using $A$ introduces some error in the ASE, 
resulting in points that lie near subspaces but not exactly on them. Using 
results from \cite{rubindelanchy2017statistical}, we can show that as $n$ 
grows, the ASE of $A$ approaches the ASE of $P$ and $B_{ij} \to 0$ for $i$ and 
$j$ in different clusters.
